Meta-analysis

### 2019-07-26 05_MetaAnalysis.Rmd
Loop to imput for both trials missing Yield_errors

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.
```{r}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          is.na(Y_error.type)) %>%
   select(Trial_ref)%>%
   distinct()
```

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(6)))
   geom_point(aes(y = log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`),
                  x = rep(0,length(log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
                  ),colour = "Black")

@@

Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`) - InterC)/ paramA

# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
hist(PM_MB_train$Yield_error)
hist(PM_MB_train$`grain_yield.t.ha.`)
hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))

PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Y_error.type <- "SamplingVariance"

>>>>

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yeild is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.
```{r}
NATrials <- PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75,
          is.na(Y_error.type)) %>%
   select(Trial_ref)%>%
   distinct()
```

@@

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(6)))

@@

for(i in NATrials$Trial_ref){
Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == i,]$`grain_yield.t.ha.`) - InterC)/ paramA

PM_MB_means[PM_MB_means$Trial_ref == i,]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == i,]$Y_error.type <- "SamplingVariance"
}
```
